% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% !Mode:: "TeX:UTF-8"

\documentclass{resume}。   
\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
\usepackage{linespacing_fix} % disable extra space before next section
\usepackage{cite}
\usepackage{setspace}
\usepackage[colorlinks,linkcolor=blue]{hyperref}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Hao Wang}
 \centerline{Senior Software Engineer}
\vspace{1ex}
\contactInfo{iamhao888@gmail.com}{WhatsApp only: +65 8357 7695}{\href{https://www.linkedin.com/in/jackkingdefier/}{LinkedIn: Hao Wang}}
 \vspace{-3ex}
 
\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Northwestern Polytechnical University (Project 985)}}{Sep. 2017 -- Apr. 2020}
  \textit{Master of Engineering} in Computer Technology, \textit{\nth{1} Prize} University Graduate Scholarship (Top 15\%)

 Relative courses: Data Mining, Probability and Mathematical Statistics, Matrix Theory, Distributed Computing.

%\vspace{1ex}
 \datedsubsection{\textbf{Northwestern Polytechnical University (Project 985)}}{Sep. 2013 -- Jun. 2017}
 \textit{Bachelor of Engineering} in Software Engineering, \textit{\nth{2} Prize} University Undergraduate Scholarship (Top 30\%)

Relative courses: Data Structures, Computer Networks, Database Systems, Object-Oriented Programming.

\section{\faUsers\ Work / Project Experience}

\datedsubsection{\textbf{Senior Software Engineer at  Daraz (Alibaba Group) Singapore}}{Oct. 2023 -- Apr. 2024}

\setlength{\parindent}{1em}
\begin{itemize}
   
    \item Designed and implemented a channel for hot-selling products using MySQL and Redis, enabling hot product tag integration and personalized recommendations.
    \item Optimized data pool refresh, reduced synchronization time from 24 hours to 1 hour, achieved an over 90\% reduction in data latency, enabled faster insights and decision-making.
     \item Enhanced user experience and boosted sales 15\% in ``11.11" shopping event by replacing new user discounts with a flexible promotion tag system based on Kubernetes and Spring Boot in the Choice channel.
    
\end{itemize}

%\datedsubsection{\textbf{Senior Software Engineer at  Daraz Hangzhou Private Limited}}{Oct. 2023 -- Jan. 2024}
%\setlength{\parindent}{1em}

%\begin{itemize}
%\item Enhanced user experience and boosted sales 15\% in ``11.11" shopping event by replacing new user discounts with a flexible promotion tag system based on Kubernetes and Spring Boot in the Choice channel.
%\end{itemize}

\datedsubsection{\textbf{Software Engineer at Alibaba (Shenzhen) Technology Co., Ltd.}}{Jul. 2021 -- Jul. 2023}

\setlength{\parindent}{1em}


\textit{\textbf{\hspace{1em}Project: Product Delivery Platform for AliExpress BU}}
% \datedsubsection{\textbf{Product Delivery Platform }}{Oct. 2022 -- now}
\begin{itemize}
  \item Optimized activity scheduling by using Redis caching and refactored the activity interface to support batch calls, reduced the average service response time by 26\%.
    \item Designed and implemented product filtering functionality using the strategy pattern, which has strong extensibility in price values and marketing type strings. Reduced the man-days required from 4 to 1.
%    \item Assumed ownership of the complete development lifecycle, spanning product ideation, design, implementation, testing, deployment, and monitoring. Collaborated extensively with cross-functional teams.
    
\end{itemize}

\textit{\textbf{Project: Social Interactive Shopping (GroupBuy, Bargain) for AliExpress BU}}
% \datedsubsection{\textbf{Social Interactive Shopping (GroupBuy, Bargain)}}{Jul. 2021 -- Sep. 2022}
\begin{itemize}
 \item Implemented mixed activities data based on cloud-native architecture, used Kafka and Redis to receive and cache items and activities. Obtained 150,000 new users in Bargain and achieved 1:7 sharing diffusion ratio.
 \item Developed and Maintained the AliExpress site-wide sharing component configuration platform.
 %, undertook large-scale marketing shopping festivals ``Double Eleven" and ``Black Friday" every year.

\end{itemize}

\datedsubsection{\textbf{Software Engineer  at vivo Mobile Communication (Shenzhen) Co., Ltd.}}{Apr. 2020 -- Jul. 2021}
\begin{itemize}
  \item Maintained Android Wifi framework and developed Wifi detection tool in OriginOS (802.11 protocol).
  \item Utilized Python to develop automated verification management tools for managing multiple mobile devices, facilitating network throughput and functionality testing.
\end{itemize}

\datedsubsection{\textbf{Graduate Research Project at Northwestern Polytechnical University}}{Oct. 2018 -- Jul. 2019}

%\setlength{\parindent}{1em}
\textit{\textbf{\hspace{1em}Project: Location Preserve Blockchain System (Crowdchain)}}
%\setlength{\parindent}{0em}

\begin{itemize}
  \item Developed Ethereum smart contracts to implement multiple scenarios of transfer functions, leveraged zero-knowledge proofs to achieve location privacy protection.
  \item Utilized web3j to establish a connection with the Rinkeby network through an Infura hosted node.
  \item Published paper as 1st author: ``Crowdchain: A location preserve anonymous payment system based on permissioned blockchain", In 2019 IEEE International Conference on Smart Internet of Things (SmartIoT).
\end{itemize}


%\section{\faTrophy\ Awards}
%\datedline{\textit{\nth{2} Prize}~~Awarded in China Graduate Contest on Smart-city Technology and Creative Design}{Jul. 2018}
%\datedline{\textit{\nth{2} Prize}~~Awarded in China Undergraduate Mathematical Contest in Modeling}{Oct. 2015}


\section{\faCogs\ Skills / Interests}
\begin{itemize}%[parsep=0.2ex]
\item Skills: Java | Python | Redis | Kafka | MySQL | Alibaba Cloud | Kubernetes | Flink | SpringBoot | Git
%  \item Experienced in continuous deployment and delivery within a microservices architecture, leveraging Spring and Spring Boot to develop distributed internet systems.(融合到skills和前面项目经历)
\item Interests: Reading | Basketball | Swimming | Lifelong learning
\end{itemize}

\clearpage

\name{王皓}
 \centerline{高级软件工程师}
\vspace{1ex}
\contactInfo{iamhao888@gmail.com}{微信 18829236977}{\href{https://github.com/JackKing-defier}{GitHub: JackKing-defier}}
 \vspace{-2ex}
 
\section{\faGraduationCap\ 教育经历}
\datedsubsection{\textbf{西北工业大学（985工程）}}{Sep. 2017 -- Apr. 2020}
 \vspace{-1ex}
\item \textit{计算机技术硕士}，一等奖学金 (Top 15\%)

相关课程：数据挖掘，概率论与数理统计，矩阵论，分布式计算，群智感知计算
\datedsubsection{\textbf{西北工业大学（985工程）}}{Sep. 2013 -- Jun. 2017}
 \vspace{-1ex}
\item \textit{软件工程学士}，二等奖学金 (Top 30\%)

相关课程：数据结构，计算机网络，数据库系统，面向对象编程，操作系统，计算机组成原理

%\vspace{1ex}
% \datedsubsection{\textbf{Northwestern Polytechnical University (Project 985)}}{Sep. 2013 -- Jun. 2017}


\section{\faUsers\ 工作和项目经历}

\datedsubsection{\textbf{Daraz Singapore（阿里旗下南亚电商）——高级软件开发工程师}}{Oct. 2023 -- Apr. 2024}

\setlength{\parindent}{1em}

\textit{\textbf{\hspace{1em}Project: 导购频道活动平台（Choice）}}
\begin{itemize}
\item 承担商品页面平台热卖商品通道的搭建，Redis 缓存优化页面配置，实现热卖商品混合召回。
\item 负责大促营销标签系统改版，使用热卖价格标签替换新老用户标签，“黑五”大促增加15\%销量。
\item 使用定时任务优化大数据平台商品数据池刷新机制，同步时间从天级别优化至1小时，将数据延迟降低90\%，支持业务快速决策调整。
    
\end{itemize}

\datedsubsection{\textbf{阿里巴巴集团（AliExpress）——软件开发工程师}}{Jul. 2021 -- Jul. 2023}

\setlength{\parindent}{1em}


\textit{\textbf{\hspace{1em}Project: 商品导购会场频道（N 元 N 件）}}
% \datedsubsection{\textbf{Product Delivery Platform }}{Oct. 2022 -- now}
\begin{itemize}
\item 个人负责重点频道NN，推动导购域所有频道响应时间性能优化专项，重构营销价格接口以支持批量调用，将N元N件频道平均服务响应时间减少26\%。
\item 投放平台升级改版核心开发，使用策略模式设计优化商品过滤功能，扩展价格和营销标签过滤。将运营配置数据发布流程所需工时从4天减少到1天。
% \item 担任完整开发生命周期的所有权，涵盖产品构思、设计、实现、测试、部署和监控。与跨职能团队广泛合作。
    
\end{itemize}

\textit{\textbf{Project: 用增团队社交互动电商（砍价/拼团）}}
% \datedsubsection{\textbf{Social Interactive Shopping (GroupBuy, Bargain)}}{Jul. 2021 -- Sep. 2022}
\begin{itemize}
\item 从0到1打造拼团项目，使用 Kafka 接收商品和活动并幂等持久化，引入 Redis 分布式缓存锁处理拼团并发问题。在砍价业务获得15万新用户，并实现1:7 分享扩散比例。
\item 独立开发维护 AliExpress 全站分享组件配置平台，支持社交互动电商页面个性化配置分享至社媒。
 %, undertook large-scale marketing shopping festivals ``Double Eleven" and ``Black Friday" every year.

\end{itemize}

\datedsubsection{\textbf{vivo 移动通信——框架开发工程师}}{Apr. 2020 -- Jul. 2021}
\begin{itemize}
\item 维护 Android Wifi 框架，OriginOS 系统中开发 Wifi 检测工具（802.11协议）。
\item 负责 vivo Y33 和 V21 机型的 Wifi 移植工作，优化 Linux 内核以增强 Wifi 吞吐量。
\end{itemize}

\datedsubsection{\textbf{硕士期间研究项目}}{Oct. 2018 -- Jul. 2019}

%\setlength{\parindent}{1em}
\textit{\textbf{\hspace{1em}Project: Location Preserve Blockchain System (Crowdchain)}}
\setlength{\parindent}{0em}

\begin{itemize}
\item 开发 Ethereum 智能合约来实现多种场景的交易功能，利用零知识证明实现了位置隐私保护。
\item 使用 web3j SDK通过 Infura 托管节点与 Rinkeby 网络建立连接。
  \item 第一作者发表会议论文: ``Crowdchain: A location preserve anonymous payment system based on permissioned blockchain", In 2019 IEEE International Conference on Smart Internet of Things (SmartIoT).
\end{itemize}


\section{\faTrophy\ Awards}
\datedline{\textit{二等奖}~~中国研究生智慧城市技术与创意设计大赛}{Jul. 2018}
\datedline{\textit{二等奖}~~中国大学生数学建模竞赛}{Oct. 2015}


\section{\faCogs\ 技能点 / 兴趣}
\begin{itemize}%[parsep=0.2ex]
\item 技术栈: Java | Python | Redis | Kafka | MySQL | Alibaba Cloud | Kubernetes | Spring | Spark | Flink | Git
%  \item Experienced in continuous deployment and delivery within a microservices architecture, leveraging Spring and Spring Boot to develop distributed internet systems.(融合到skills和前面项目经历)
\item 兴趣爱好: 阅读 | 篮球 | 游泳 | 终生学习
\end{itemize}



\end{document}
