% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% !Mode:: "TeX:UTF-8"

\documentclass{resume}。   
\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
\usepackage{linespacing_fix} % disable extra space before next section
\usepackage{cite}
\usepackage{setspace}
\usepackage[colorlinks,linkcolor=blue]{hyperref}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Hao Wang}
 \centerline{Senior Software Engineer}
\vspace{1ex}
\contactInfo{iamhao888@gmail.com}{WeChat +86 18829236977}{\href{https://www.linkedin.com/in/jackkingdefier/}{LinkedIn: Hao Wang}}
 \vspace{-3ex}
 
\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Northwestern Polytechnical University (Project 985)}}{Sep. 2017 -- Apr. 2020}
  \textit{Master of Engineering} in Computer Technology, \textit{\nth{1} Prize} University Graduate Scholarship (Top 15\%)

 Relative courses: Data Mining, Probability and Mathematical Statistics, Matrix Theory, Distributed Computing.

%\vspace{1ex}
 \datedsubsection{\textbf{Northwestern Polytechnical University (Project 985)}}{Sep. 2013 -- Jun. 2017}
 \textit{Bachelor of Engineering} in Software Engineering, \textit{\nth{2} Prize} University Undergraduate Scholarship (Top 30\%)

Relative courses: Data Structures, Computer Networks, Database Systems, Object-Oriented Programming.

\section{\faUsers\ Work / Project Experience}

\datedsubsection{\textbf{Senior Software Engineer at  Daraz (Alibaba Group) Singapore}}{Oct. 2023 -- Apr. 2024}

\setlength{\parindent}{1em}
\begin{itemize}
   
    \item Leveraged MySQL and Redis to design and implement a scalable product-building platform, enabling real-time integration of hot product tags and personalized recommendations. Implemented cloud-native architecture to ensure high availability and scalability.
    \item Replaced new user discounts with a Kubernetes-based promotion tag system using Spring Boot, improving system resilience and boosting sales by 15\%.
     \item Optimized data synchronization with ScheduleX tasks, reducing refresh time from 24 hours to 1 hour and enhancing data consistency across cloud environments.
    
\end{itemize}

%\datedsubsection{\textbf{Senior Software Engineer at  Daraz Hangzhou Private Limited}}{Oct. 2023 -- Jan. 2024}
%\setlength{\parindent}{1em}

%\begin{itemize}
%\item Enhanced user experience and boosted sales 15\% in ``11.11" shopping event by replacing new user discounts with a flexible promotion tag system based on Kubernetes and Spring Boot in the Choice channel.
%\end{itemize}

\datedsubsection{\textbf{Software Engineer at Alibaba (Shenzhen) Technology Co., Ltd.}}{Jul. 2021 -- Jul. 2023}

\setlength{\parindent}{1em}


\textit{\textbf{\hspace{1em}Project: Product Delivery Platform for AliExpress BU}}
% \datedsubsection{\textbf{Product Delivery Platform }}{Oct. 2022 -- now}
\begin{itemize}
%  \item Optimized activity scheduling by using Redis caching and refactored the activity interface to support batch calls, reduced the average service response time by 26\%.
    \item Developed a flexible product filtering system using the strategy pattern with strong extensibility for price values and marketing strategies. Incorporated cloud-native best practices to reduce man-days from 4 to 1 for deployment.
    \item Assumed ownership of the complete development lifecycle, spanning product ideation, design, implementation, testing, deployment, and monitoring. Collaborated extensively with cross-functional teams.
    
\end{itemize}

\textit{\textbf{Project: Social Interactive Shopping (GroupBuy, Bargain) for AliExpress BU}}
% \datedsubsection{\textbf{Social Interactive Shopping (GroupBuy, Bargain)}}{Jul. 2021 -- Sep. 2022}
\begin{itemize}
 \item Implemented mixed activities data based on cloud-native architecture, used Kafka and Redis to receive and cache items and activities. Obtained 150,000 new users in Bargain and achieved 1:7 sharing diffusion ratio.
 \item Developed and Maintained the AliExpress site-wide sharing component configuration platform.
 %, undertook large-scale marketing shopping festivals ``Double Eleven" and ``Black Friday" every year.

\end{itemize}

\datedsubsection{\textbf{Software Engineer  at vivo Mobile Communication (Shenzhen) Co., Ltd.}}{Apr. 2020 -- Jul. 2021}
\begin{itemize}
  \item Maintained and optimized the Android Wifi framework, improving network throughput and reliability by focusing on 802.11 protocol enhancements and Linux kernel optimizations.
  \item Developed automated testing frameworks using Python to facilitate network throughput and functional testing across multiple devices, streamlining testing operations.
\end{itemize}

\datedsubsection{\textbf{Graduate Research Project at Northwestern Polytechnical University}}{Oct. 2018 -- Jul. 2019}

%\setlength{\parindent}{1em}
\textit{\textbf{\hspace{1em}Project: Location Preserve Blockchain System (Crowdchain)}}
%\setlength{\parindent}{0em}

\begin{itemize}
  \item Developed Ethereum smart contracts to implement multiple scenarios of transfer functions, leveraged zero-knowledge proofs to achieve location privacy protection.
  \item Utilized web3j to establish a connection with the Rinkeby network through an Infura hosted node.
  \item Published paper as 1st author: ``Crowdchain: A location preserve anonymous payment system based on permissioned blockchain", In 2019 IEEE International Conference on Smart Internet of Things (SmartIoT).
\end{itemize}


%\section{\faTrophy\ Awards}
%\datedline{\textit{\nth{2} Prize}~~Awarded in China Graduate Contest on Smart-city Technology and Creative Design}{Jul. 2018}
%\datedline{\textit{\nth{2} Prize}~~Awarded in China Undergraduate Mathematical Contest in Modeling}{Oct. 2015}


\section{\faCogs\ Skills / Interests}
\begin{itemize}%[parsep=0.2ex]
\item Skills: Java | Python | Redis | Kafka | MySQL | Alibaba Cloud | CI/CD | Kubernetes | Flink | SpringBoot
%  \item Experienced in continuous deployment and delivery within a microservices architecture, leveraging Spring and Spring Boot to develop distributed internet systems.(融合到skills和前面项目经历)
\item Interests: Reading | Basketball | Swimming | Lifelong learning
\end{itemize}

\end{document}
