% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% !Mode:: "TeX:UTF-8"

\documentclass{resume}
\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
\usepackage{linespacing_fix} % disable extra space before next section
\usepackage{cite}
\usepackage{setspace}
\usepackage[colorlinks,linkcolor=blue]{hyperref}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Hao Wang}
 \centerline{Senior Software Engineer}
\vspace{1ex}
\contactInfo{iamhao888@gmail.com}{(+65) 8357-7695}{\href{https://github.com/JackKing-defier}{GitHub: JackKing-defier}}
 \vspace{-3ex}
 
\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Northwestern Polytechnical University (Project 985)}}{Sep. 2017 -- Apr. 2020}
  \textit{Master of Engineering} in Computer Technology, \textit{\nth{1} Prize} University Graduate Scholarship (Top 15\%)

 Relative courses: Data Mining, Probability and Mathematical Statistics, Matrix Theory, Distributed Computing.

%\vspace{1ex}
 \datedsubsection{\textbf{Northwestern Polytechnical University (Project 985)}}{Sep. 2013 -- Jun. 2017}
 \textit{Bachelor of Engineering} in Software Engineering, \textit{\nth{2} Prize} University Undergraduate Scholarship (Top 30\%)

Relative courses: Data Structures, Computer Networks, Database Systems, Object-Oriented Programming.

\section{\faUsers\ Work / Project Experience}

\datedsubsection{\textbf{Senior Software Engineer at  Daraz Singapore Private Limited}}{Oct. 2023 -- Apr. 2024}

\setlength{\parindent}{1em}

\textit{\textbf{\hspace{1em}Project: Global Campaign Platform for Daraz BU}}
\begin{itemize}
  \item Designed and implemented a product building platform channel with MySQL and Redis, enabling hot product tag integration and personalized recommendations.
    \item Enhanced user experience and boosted sales 15\% by replacing new user discounts with a flexible promotion tag system based on Kubernetes and Spring Boot in the Choice channel.
    \item Optimized data pool refresh, reduced synchronization time from 24 hours to 1 hour, achieved an over 90\% reduction in data latency, enabled faster insights and decision-making.
    
\end{itemize}

\datedsubsection{\textbf{Software Engineer at Alibaba (Shenzhen) Technology Co., Ltd.}}{Jul. 2021 -- Jul. 2023}

\setlength{\parindent}{1em}


\textit{\textbf{\hspace{1em}Project: Product Delivery Platform for AliExpress BU}}
% \datedsubsection{\textbf{Product Delivery Platform }}{Oct. 2022 -- now}
\begin{itemize}
  \item Optimized activity scheduling by using Redis caching and refactored the activity interface to support batch calls, reduced the average service response time by 26\%.
    \item Designed and implemented product filtering functionality using the strategy pattern, which has strong extensibility in price values and marketing type strings. Reduced the man-days required from 4 to 1.
%    \item Assumed ownership of the complete development lifecycle, spanning product ideation, design, implementation, testing, deployment, and monitoring. Collaborated extensively with cross-functional teams.
    
\end{itemize}

\textit{\textbf{Project: Social Interactive Shopping (GroupBuy, Bargain) for AliExpress BU}}
% \datedsubsection{\textbf{Social Interactive Shopping (GroupBuy, Bargain)}}{Jul. 2021 -- Sep. 2022}
\begin{itemize}
 \item Implemented mixed activities data based on cloud-native architecture, used Kafka and Redis to receive and cache items and activities. Obtained 150,000 new users in Bargain and achieved 1:7 sharing diffusion ratio.
 \item Developed and Maintained the AliExpress site-wide sharing component configuration platform.
 %, undertook large-scale marketing shopping festivals ``Double Eleven" and ``Black Friday" every year.

\end{itemize}

\datedsubsection{\textbf{Software Engineer  at vivo Mobile Communication (Shenzhen) Co., Ltd.}}{Apr. 2020 -- Jul. 2021}
\begin{itemize}
  \item Maintained Android Wifi framework and developed Wifi detection tool in OriginOS (802.11 protocol).
  \item Led Wifi porting for vivo Y33 and V21 smartphones, optimized Linux kernel to enhance Wifi throughput.
  \item Utilized Python to develop automated testing tools for managing multiple mobile devices, facilitating network throughput and functionality testing.
\end{itemize}

\datedsubsection{\textbf{Graduate Research Project at Northwestern Polytechnical University}}{Oct. 2018 -- Jul. 2019}

%\setlength{\parindent}{1em}
\textit{\textbf{\hspace{1em}Project: Location Preserve Blockchain System (Crowdchain)}}
\setlength{\parindent}{0em}

\begin{itemize}
  \item Developed Ethereum smart contracts to implement multiple scenarios of transfer functions, leveraged zero-knowledge proofs to achieve location privacy protection.
  \item Utilized web3j to establish a connection with the Rinkeby network through an Infura hosted node.
  \item Published paper as 1st author: ``Crowdchain: A location preserve anonymous payment system based on permissioned blockchain", In 2019 IEEE International Conference on Smart Internet of Things (SmartIoT).
\end{itemize}


%\section{\faTrophy\ Awards}
%\datedline{\textit{\nth{2} Prize}~~Awarded in China Graduate Contest on Smart-city Technology and Creative Design}{Jul. 2018}
%\datedline{\textit{\nth{2} Prize}~~Awarded in China Undergraduate Mathematical Contest in Modeling}{Oct. 2015}


\section{\faCogs\ Skills / Interests}
\begin{itemize}%[parsep=0.2ex]
\item Skills: Java | Python | Redis | Kafka | MySQL | Alibaba Cloud | Kubernetes | Flink | SpringBoot | Git
%  \item Experienced in continuous deployment and delivery within a microservices architecture, leveraging Spring and Spring Boot to develop distributed internet systems.(融合到skills和前面项目经历)
\item Interests: Reading | Basketball | Swimming | Lifelong learning
\end{itemize}

\end{document}
